prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-05 inst/MyArticle/paper.Rmd
Text cosmetics R6

Using the tidy table to model the data ensures interoperability with other proteomics-related packages that manage their data with tidy-tables, e.g., `r BiocStyle::CRANpkg("protti")`. Furthermore, the use of `R6` classes, which encapsulate the configuration and the data, allows writing very concise code (no function arguments needed), and auto-completion support in the Rstudio editor makes it easy for novices to explore `r BiocStyle::Githubpkg("fgcz/prolfqua")`s functionality.

>>>>

Using the tidy table to model the data ensures interoperability with other proteomics-related packages that manage their data with tidy-tables, e.g., `r BiocStyle::CRANpkg("protti")`. Furthermore, the consistent implementation of `R6` classes, which encapsulate the configuration and the data, allows writing very concise code (no function arguments needed), and auto-completion support in the Rstudio editor makes it easy for novices to explore `r BiocStyle::Githubpkg("fgcz/prolfqua")`s functionality.
